Super awesome embeddings

### 2019-02-03 paper/main.tex
Add abstract

\begin{document}
\maketitle
\begin{abstract}
Abstract
\keywords{word sense disambiguation, word embeddings}

\end{abstract}

>>>>

\begin{document}
\maketitle
\begin{abstract}

In recent years word embeddings have been shown to boost the performance in NLP tasks such as syntactic parsing or sentiment analysis, but also in multimodal systems like image captioning or visual question answering. It is therefore not surprising that word embeddings have been applied to Word Sense Disambiguation (WSD) problem as well. In this work, we present how a simple word embeddings average based method can be used to produce keyword (meaning) and context embeddings and how the former can be improved with two embeddings distance optimization techniques.

We also open source dataset we've created for our experiments. It is composed of 6 ambiguous words, with 4 to 7 meanings each, and collected real-world usage examples of those meanings, with tagged words to be disambiguated.

\keywords{word sense disambiguation}
\end{abstract}
